Regression

### 2018-02-11 paper/R/04_Modelresults.Rmd
30 topics

# 3. Model Results
```{r caching, echo = FALSE}
load("../output/models/STM_ownership 40 .Rda")
```

@@

After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
```{r}
sagelabs$cov.betas[[2]]$problabels[,1:5]
```

```{r}
topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition", 
                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder", 
                   7, "political trends after the election", 8, "Merkel vs.Schulz", 
                   9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
                   11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
                   12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg", 
                   15, "error (text processing failure)", 16, "Police academy (Berlin), AfD", 
                   17, "Federal budget statistics", 18, "Family reunion refugees", 
                   19, "Polls federal election", 20, "AfD in social media", 
                   21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
                   23, "Court sentences, NSU trial", 24, "election campaigns & political talkshows", 
                   25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
                   28, "Turkey, Russia", 29, "A.Merkel in east GER", 30, "H.Kohl obituary", 
                   31, "AfD (Petri, Gauland, Höcke)", 32, "Asylum claims and deportation", 
                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
                   37, "AfD in parliament", 38, "Church", 39, "Terror attacks (GER)  & police reports", 
                   40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)

topics.df <- as.data.frame(topics) %>%
  transmute(topic_name = paste(V1, V2, sep=": "),
         topic = 1:40) 
```

@@

for(i in 2:40) {
  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
  freq1 <- as.data.frame(freq1) %>% 
    transmute(ownership=stmOut$settings$covariates$yvarlevels,
           topic = i,
           freq = freq1)

@@

ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
dpi = 600)
```

@@

```{r}
# effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
#                          metadata = out$meta, uncertainty = "None")

effect <- estimateEffect(c(1:40) ~ownership+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
#save(out_ownership,stmOut, effect, file = "stm_newsdata.RData")
```

@@

ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 7,
dpi = 600)
```

@@

## 3.3 Topic Correlation
```{r}
## Create Dataframe with correlations
cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
colnames(cor) <- 1:40

df <- as.data.frame(cor) %>% 
  mutate(topic = 1:40) %>%
  melt(., id="topic", value.name="corr") %>%
  mutate(site = stmOut$settings$covariates$yvarlevels[1])

for (i in 2:2) {
  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
  colnames(cor) <- 1:40

  df1 <- as.data.frame(cor) %>%
    mutate(topic = 1:40) %>%
    melt(., id="topic", value.name="corr") %>%
    mutate(site = stmOut$settings$covariates$yvarlevels[i])

@@

```{r}
plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[29,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[29,], collapse="\n")))
```

>>>>

# 3. Model Results
```{r caching, echo = FALSE}
load("../output/models/STM_ownership 30 .Rda")
k <- stmOut$settings$dim$K
```

@@

After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
```{r}
sagelabs$cov.betas[[1]]$problabels[,1:5]
```

```{r}
topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Coalition talks (Jamaica, Niedersachsen)", 
                   4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "DIE LINKE", 
                   7, "Islam and antisemitism in GER", 8, "Merkel vs.Schulz", 
                   9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
                   11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
                   12, "Federal Election trends", 13, "EU policies", 14, "G20 Hamburg", 
                   15, "error (text processing failure)", 16, "Refugees, asylum claims", 
                   17, "Budget statistics, social welfare", 18, "Jamaica Coalition talks", 
                   19, "Polls federal election", 20, "AfD in social media", 
                   21, "Women empowerment, M.Schwesig (SPD)", 22, "AfD (Petri, Gauland, Höcke)", 
                   23, "Terror attack Berlin (Amri)", 24, "election campaigns & political talkshows", 
                   25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
                   28, "Turkey, Russia", 29, "Terror attacks (GER)  & police reports", 30, "H.Kohl obituary"), ncol=2, byrow=T)

# topics <- matrix(c(1, "Great coalition", 2, "A.Merkel, CSU, Guttenberg", 3, "Jamaica coalition", 
#                    4, "Diesel scandal", 5, "A.Merkel, glyphosat scandal", 6, "Seehover vs. Söder", 
#                    7, "political trends after the election", 8, "Merkel vs.Schulz", 
#                    9, "Trends in electoral districts", 10, "Steinmeier, Federal President", 
#                    11, "G.Schröder & IT themes (Data policy, Wifi, Telekom)", 
#                    12, "Federal Election trends", 13, "Climate policy, Die Grünen", 14, "G20 Hamburg", 
#                    15, "error (text processing failure)", 16, "Police academy (Berlin), AfD", 
#                    17, "Federal budget statistics", 18, "Family reunion refugees", 
#                    19, "Polls federal election", 20, "AfD in social media", 
#                    21, "Women empowerment, M.Schwesig (SPD)", 22, "elections in Niedersachsen", 
#                    23, "Court sentences, NSU trial", 24, "election campaigns & political talkshows", 
#                    25, "German armed forces", 26, "Issues in the Bundestag", 27, "C.Lindner FDP", 
#                    28, "Turkey, Russia", 29, "A.Merkel in east GER", 30, "H.Kohl obituary", 
#                    31, "AfD (Petri, Gauland, Höcke)", 32, "Asylum claims and deportation", 
#                    33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
#                    37, "AfD in parliament", 38, "Church", 39, "Terror attacks (GER)  & police reports", 
#                    40, "DHL package attack (Potsdam)"), ncol=2, byrow=T)

topics.df <- as.data.frame(topics) %>%
  transmute(topic_name = paste(V1, V2, sep=": "),
         topic = 1:k) 
```

@@

for(i in 2:k) {
  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
  freq1 <- as.data.frame(freq1) %>% 
    transmute(ownership=stmOut$settings$covariates$yvarlevels,
           topic = i,
           freq = freq1)

@@

# ggsave(filename = "../figs/topic_proportion.png", device = "png",width = 12, height = 10,
# dpi = 600)
```

@@

```{r}
effect <- estimateEffect(c(1:k) ~ownership+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
#save(out_ownership,stmOut, effect, file = "stm_newsdata.RData")
```

@@

# ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 7,
# dpi = 600)
```

@@

## 3.3 Topic Correlation
```{r}
## Create Dataframe with correlations
cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
colnames(cor) <- 1:k

df <- as.data.frame(cor) %>% 
  mutate(topic = 1:k) %>%
  melt(., id="topic", value.name="corr") %>%
  mutate(site = stmOut$settings$covariates$yvarlevels[1])

for (i in 2:2) {
  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
  colnames(cor) <- 1:k

  df1 <- as.data.frame(cor) %>%
    mutate(topic = 1:k) %>%
    melt(., id="topic", value.name="corr") %>%
    mutate(site = stmOut$settings$covariates$yvarlevels[i])

@@

```{r}
plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[27,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[27,], collapse="\n")))
```
